(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-04 ms.tex
Section 5 done, modulo one maybe subsection.

Cite \citet{Coughlin14} and \citet{Batalha13} in here.

@@

We do not detect any significant transit timing variations

@@

>>>>

Such effects are not uncommon in \kep\ data. 
\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
ephemerides between candidates. 
In that paper, the authors limited their search to candidates within $20\arcsec$ of other
objects of interest. 
\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and 
outlining four physical reasons why these anomalies may occur.
While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
explained by any one of the effects described by \citet{Coughlin14} alone. 
This artifact should be carefully studied in the future, as it may help illuminate other 
potential detector artifacts, both in \kep\ and \KT\ data.

@@

We do not detect any significant transit timing variations (TTVs) in any of these systems from 
the \KT\ data alone. 
EPIC 201338508 would be expected to have a TTV period of 117 days, but 
is likely too far from commensurability to have an observable TTV signal. 
EPIC 201445392 is expected to have a TTV period of 234 days, so this system may be a candidate
for additional follow-up to constrain the system masses dynamically. 
The transiting planets orbiting EPIC 201754305 are near a 5:2 period commensurability. 
There is no evidence from \kep\ of an abundance of planets near this period ratio, and so this 
may be coincidence.
Follow-up observations may be warranted to search for an additional planet in this system 
forming a resonant chain, similar to those observed around other stars \citep[e.g.][]{Swift13,
Campante15}.

@@

One of the primary goals of \KT\ is the detection of transiting planets around bright stars that
can be followed up from the ground or with future space-based observatories such as JWST 
\citep{Howell14}. 
Of our sample, two systems orbit stars with $K < 9$: EPIC 201367065 \citep{Crossfield15} and
EPIC 201912552. 
An additional four targets orbit stars with $K <10$. 
These targets are ideal for ground-based followup, and may be useful targets for Spitzer and 
JWST to probe planetary atmospheres.
